---
title: "Your Title"
output: 
  pdf_document:
    latex_engine: xelatex
  html_document: default
---
# Setup and Data Loading
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,     # Hide warnings
  message = FALSE,     # Hide messages
  echo = TRUE,         # Show code by default
  results = "markup"   # Show results by default
)
```

```{r include=FALSE}
# Load necessary libraries
library(tidyverse)  # For data manipulation
library(tidytext)
library(car)        # For diagnostic tests
library(lmtest)     # For model diagnostics
library(betareg)    # For beta regression
library(ggplot2)    # For visualisations
library(ggeffects)
library(psych)      # For factor analysis
library(lmtest)     # For model comparison tests
library(tidyr)      # For data manipulation
library(purrr)      # For functional programming

# Read the data
setwd("C:/Users/Gairui/OneDrive - University College London/Dissertation/Data Analysis")
# If using RDS format (as mentioned in your documentation)
steam_data <- readRDS("Steam_data_gametags.rds")
```

# Data Preparation
```{r}
# Data preparation
steam_data <- steam_data %>%
  # Create the dependent variable 'sc_ratio'
  mutate(
    sc_ratio = schinese_reviews / total_reviews,
    # Convert boolean variable to numeric dummy (1 = TRUE, 0 = FALSE)
    chinese_simplified_interface_subtitles_dummy = as.numeric(chinese_simplified_interface_subtitles)
  )

# Check for missing values in key variables
sum(is.na(steam_data$sc_ratio))
sum(is.na(steam_data$chinese_simplified_interface_subtitles_dummy))

# Explore the dependent variable
summary(steam_data$sc_ratio)
hist(steam_data$sc_ratio, main = "Distribution of Chinese Reviews Ratio", 
     xlab = "Ratio of Chinese Reviews to Total Reviews")

# Count exact zeros and ones
sum(steam_data$sc_ratio == 0)
sum(steam_data$sc_ratio == 1)

# Log transformation for dependent variable
steam_data <- steam_data %>%
  mutate(
    sc_ratio_adj = case_when(
      sc_ratio == 0 ~ 0.00001,
      sc_ratio == 1 ~ 0.99999,
      TRUE ~ sc_ratio
    ),
    sc_ratio_logit = log(sc_ratio_adj / (1 - sc_ratio_adj))
  )

# Log transformations for total review
steam_data <- steam_data %>%
  mutate(
    log_total_reviews = log(total_reviews)
  )
```

The histogram reveals a highly skewed distribution of the Chinese reviews ratio, with the majority of observations 
clustered near zero and a small uptick at 1.0. This distinctive pattern demonstrates why standard OLS regression 
would be inappropriate for several reasons:\
Non-normality: The severe right-skew violates the OLS assumption of normally distributed residuals.\
Bounded response variable: As a proportion confined to the [0,1] interval, OLS could produce meaningless predictions outside this range.\
Heteroscedasticity: The variance likely changes across the range of predictors, evidenced by the concentrated values near 
zero and sparse distribution elsewhere.\
Boundary values: The presence of exact zeros and ones creates problems for many statistical techniques.

# Tag Analysis
```{r}
# Function to extract tags from each game
extract_tags <- function(tag_string) {
  # Remove brackets and split by commas followed by spaces
  tags <- gsub("\\[|\\]", "", tag_string) %>%
    strsplit("', '") %>%
    unlist()
  
  # Clean up any remaining quotes
  tags <- gsub("^'|'$", "", tags)
  return(tags)
}

# Extract and count individual tags
all_individual_tags <- steam_data %>%
  mutate(game_tags = as.character(game_tags)) %>%
  rowwise() %>%
  mutate(extracted_tags = list(extract_tags(game_tags))) %>%
  # Unnest the extracted tags
  unnest(extracted_tags) %>%
  # Count frequency of each tag
  count(extracted_tags, sort = TRUE) %>%
  rename(Tag = extracted_tags, Frequency = n)

# Create a dataframe for better viewing
tag_df <- data.frame(
  Tag = all_individual_tags$Tag,
  Frequency = all_individual_tags$Frequency,
  Percentage = round(all_individual_tags$Frequency / nrow(steam_data) * 100, 2)
)

# Display top 200 tags
top_200_tags <- head(all_individual_tags, 200)
print(top_200_tags)

# Save the top 100 tag frequency table
write.csv(top_200_tags, "top_200_game_tags.csv", row.names = FALSE)

# Plot top 20 tags
ggplot(head(tag_df, 20), aes(x = reorder(Tag, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 20 Game Tags on Steam",
       x = "Tag",
       y = "Frequency") +
  theme_minimal()
```

# Create dummy variables for major genres
```{r}
steam_data <- steam_data %>%
  mutate(
    has_action = as.numeric(grepl("Action", game_tags, ignore.case = TRUE)),
    has_adventure = as.numeric(grepl("Adventure", game_tags, ignore.case = TRUE)),
    has_rpg = as.numeric(grepl("RPG", game_tags, ignore.case = TRUE)),
    has_story_rich = as.numeric(grepl("Story Rich", game_tags, ignore.case = TRUE)),
    has_strategy = as.numeric(grepl("Strategy", game_tags, ignore.case = TRUE)),
    has_casual = as.numeric(grepl("Casual", game_tags, ignore.case = TRUE)),
    has_simulation = as.numeric(grepl("Simulation", game_tags, ignore.case = TRUE)),
    has_anime = as.numeric(grepl("Anime", game_tags, ignore.case = TRUE)),
    has_puzzle = as.numeric(grepl("Puzzle", game_tags, ignore.case = TRUE))
  )
```

# Initial Models
```{r}
# Simple OLS model
model0 <- lm(sc_ratio ~ chinese_simplified_interface_subtitles_dummy, data = steam_data)
summary(model0)

# Dependent variable log model
model1 <- lm(sc_ratio_logit ~ chinese_simplified_interface_subtitles_dummy, data = steam_data)
summary(model1)

# Checking OLS assumptions
# 1. Linearity - Not applicable for binary predictors
# 2. Independence - Assumed based on data collection methodology
# 3. Homoscedasticity
par(mfrow = c(2, 2))
plot(model0, main = "OLS Model")
par(mfrow = c(2, 2))
plot(model1, main = "Logit-transformed OLS")
par(mfrow = c(1, 1))

# Formal test for heteroscedasticity using Breusch-Pagan test
bp_test_model0 <- bptest(model0)
print(bp_test_model0)

bp_test_model1 <- bptest(model1)
print(bp_test_model1)

# Beta regression model
model2 <- betareg(sc_ratio_adj ~ chinese_simplified_interface_subtitles_dummy, data = steam_data)
summary(model2)
plot(model2)
```

The comparative analysis of simple regression models reveals clear limitations in modelling proportion data with standard approaches.\
The baseline OLS model confirms that games with simplified Chinese interface/subtitles have a significantly higher ratio of Chinese reviews 
(21.23 percentage points higher) compared to games without this localisation feature. This substantial effect is highly statistically significant
 (p<0.001) and explains approximately 20% of the variation in Chinese review ratio (R²=0.1998).\
The logit-transformed model improves fit somewhat (R²=0.2572), demonstrating that the transformation better accommodates the bounded nature of 
the proportion data. The coefficient estimate (2.77) on the logit scale indicates that Chinese localisation dramatically shifts the odds of 
receiving Chinese reviews.\
However, both models exhibit problematic residual patterns. The OLS model cannot account for the [0,1] constraint of proportions, 
while the logit transformation's effectiveness is limited by the high concentration of values near zero. These findings justify 
exploring beta regression, which is specifically designed for continuous proportion data with these distributional characteristics.

# Model Comparison 123
```{r}
# Compare model fit
# For OLS models, extract R-squared
r2_model0 <- summary(model0)$r.squared
r2_model1 <- summary(model1)$r.squared

# For beta regression, extract pseudo R-squared
r2_model2 <- summary(model2)$pseudo.r.squared

# Create comparison table
model_comparison <- data.frame(
  Model = c("Standard OLS", "Logit-transformed OLS", "Beta Regression"),
  R_squared = c(r2_model0, r2_model1, r2_model2),
  AIC = c(AIC(model0), AIC(model1), AIC(model2))
)
print(model_comparison)

# Compare coefficient estimates
coef_model0 <- coef(model0)[2]  # Extract coefficient for localisation dummy
coef_model1 <- coef(model1)[2]  # For logit model
coef_model2 <- coef(model2)[2]  # For beta model (mean submodel)

# Create coefficient comparison
coef_comparison <- data.frame(
  Model = c("Standard OLS", "Logit-transformed OLS", "Beta Regression"),
  Coefficient = c(coef_model0, coef_model1, coef_model2)
)
print(coef_comparison)

# Compare predicted vs actual values
steam_data <- steam_data %>%
  mutate(
    pred_model0 = predict(model0),
    pred_model1 = predict(model1),
    pred_model2 = predict(model2, type = "response")
  )

# Correlation between predicted and actual values
cor_model0 <- cor(steam_data$sc_ratio, steam_data$pred_model0)
cor_model1 <- cor(steam_data$sc_ratio, exp(steam_data$pred_model1)/(1+exp(steam_data$pred_model1)))
cor_model2 <- cor(steam_data$sc_ratio, steam_data$pred_model2)

pred_comparison <- data.frame(
  Model = c("Standard OLS", "Logit-transformed OLS", "Beta Regression"),
  Correlation = c(cor_model0, cor_model1, cor_model2)
)
print(pred_comparison)
```

Three modelling approaches were compared to determine the most appropriate method for analysing the Chinese reviews ratio:\

Standard OLS: Explains approximately 20.0% of variance (R² = 0.1998), with a localisation dummy coefficient of 0.21.\
Logit-transformed OLS: Explains approximately 25.7% of variance (R² = 0.2572), with a much larger coefficient (2.77) due to the logit transformation scale.\
Beta Regression: Also explains 25.7% of variance with a coefficient of 1.11 for the localisation dummy.\

The Beta Regression model demonstrates dramatically superior fit with the lowest AIC value (-33774.72), compared to Standard OLS (-3691.42) and the poorly performing Logit-transformed OLS (64512.00).

# Enhanced Models with Control Variables
```{r}
# Adding released year as a control variable
# Extract year from release_date
steam_data <- steam_data %>%
  mutate(
    # Extract year from release_date (first 4 characters)
    release_year = as.factor(substr(release_date, 1, 4))
  )
# Check the distribution of years
table(steam_data$release_year)

# Beta regression with year fixed effects
model3 <- betareg(sc_ratio_adj ~ chinese_simplified_interface_subtitles_dummy + release_year, 
                  data = steam_data)
summary(model3)
exp(coef(model3)[1:2])

# Create 'has_indie' dummy
steam_data <- steam_data %>%
  mutate(
    has_indie = as.numeric(grepl("Indie", game_tags, ignore.case = TRUE))
  )

# Create categorical localisation variable for SC
steam_data <- steam_data %>%
  mutate(
    sc_localisation_combo = case_when(
      chinese_simplified_audio & chinese_simplified_interface_subtitles ~ "Audio + Text",
      chinese_simplified_audio & !chinese_simplified_interface_subtitles ~ "Audio Only",
      !chinese_simplified_audio & chinese_simplified_interface_subtitles ~ "Text Only",
      TRUE ~ "None"
    )
  )

# Create combined Chinese localisation variable (SC or TC)
steam_data <- steam_data %>%
  mutate(
    full_localisation_combo = case_when(
      # Audio + Text: Either SC or TC audio AND either SC or TC text/subtitles
      (chinese_simplified_audio | chinese_traditional_audio) & 
        (chinese_simplified_interface_subtitles | chinese_traditional_interface_subtitles) ~ "Audio + Text",
      
      # Audio Only: Either SC or TC audio but no Chinese text/subtitles
      (chinese_simplified_audio | chinese_traditional_audio) & 
        !(chinese_simplified_interface_subtitles | chinese_traditional_interface_subtitles) ~ "Audio Only",
      
      # Text Only: Either SC or TC text/subtitles but no Chinese audio
      !(chinese_simplified_audio | chinese_traditional_audio) & 
        (chinese_simplified_interface_subtitles | chinese_traditional_interface_subtitles) ~ "Text Only",
      
      # None: No Chinese localisation at all
      TRUE ~ "None"
    )
  )

# Beta regression with categorical localisation
model4 <- betareg(sc_ratio_adj ~ factor(sc_localisation_combo) + release_year, data = steam_data)
summary(model4)
exp(coef(model4)[1:3])
```

Localisation Effects:

Games with no Chinese localisation show dramatically lower proportions of Chinese reviews compared to the reference 
category of "Audio + Text" (coefficient: -1.368, p < 2e-16)\
Games with "Text Only" localisation also show significantly lower proportions, though the effect is less severe (coefficient: -0.318, p < 2e-16)

Odds Ratios:

Converting to odds ratios reveals that games with no localisation have approximately 74.5% lower odds (odds ratio: 0.255) 
of Chinese reviews compared to fully localised games\
Games with text-only localisation have approximately 27.2% lower odds (odds ratio: 0.728) compared to games with full audio and text localisation

Release Year Effects:

Surprisingly, none of the release year coefficients reach statistical significance, suggesting the proportion of Chinese reviews is relatively 
stable across different release years when controlling for localisation

# Models with Price Variables
```{r}
# Convert price_cny to numeric (handle "Free" or "Unknown")
steam_data <- steam_data %>%
  mutate(
    price_cny_numeric = case_when(
      price_cny == "Free" ~ 0,
      price_cny == "Unknown" ~ NA_real_,
      TRUE ~ as.numeric(price_cny)
    )
  )

# Convert price_usd to numeric (handle "Free" or "Unknown")
steam_data <- steam_data %>%
  mutate(
    price_usd_numeric = case_when(
      price_usd == "Free" ~ 0,
      price_usd == "Unknown" ~ NA_real_,
      TRUE ~ as.numeric(price_usd)
    )
  )

# Check for missing values
sum(is.na(steam_data$price_cny_numeric))
sum(is.na(steam_data$price_usd_numeric))

# Beta regression with categorical localisation + price_cny/usd
model5 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year + price_cny_numeric, 
  data = steam_data
)
summary(model5)

model6 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year + price_usd_numeric, 
  data = steam_data
)
summary(model6)

# Check AIC/BIC for model comparison
AIC(model4, model5, model6)
BIC(model4, model5, model6)
```

# Models with Indie Game Variable
```{r}
# Verify distribution
table(steam_data$has_indie)  # Check counts of 0 vs. 1

# Beta regression with indie dummy
model7 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year + has_indie, 
  data = steam_data
)
summary(model7)

#AIC and BIC test for model 4 and 7
AIC(model4, model7)
BIC(model4, model7)

# Adding interaction for indie and SC localisation level
model8 <- betareg(sc_ratio_adj ~ factor(sc_localisation_combo)*has_indie + release_year, data = steam_data)
summary(model8)

#Visualize interaction effects
ggplot(steam_data, aes(x = sc_localisation_combo, 
                       y = sc_ratio_adj, 
                       color = factor(has_indie),
                       group = interaction(sc_localisation_combo, has_indie))) +
  geom_boxplot() +
  labs(title = "Effect of Localisation on Chinese Reviews (Indie vs. Non-Indie)",
       x = "Simplified Chinese Localization",
       y = "Adjusted Chinese Review Ratio",
       color = "Indie Game") +
  scale_color_discrete(labels = c("Non-Indie", "Indie")) +
  theme_minimal()

#AIC and BIC test for model 4 and 8
AIC(model4, model8)
BIC(model4, model8)

# LRT test for model 4 and 8
lrt_result_48 <- lrtest(model4, model8)
print(lrt_result_48)
```

Model 7 tests the direct effect of indie status alongside localisation type and release year. The results show significant effects for localisation levels, 
with games lacking any Chinese localisation having substantially lower Chinese review ratios (coefficient = -1.368, p < 0.001) compared to fully localised 
games (audio + text). Games with text-only localisation also show significantly lower ratios (coefficient = -0.318, p < 0.001), though the effect is less 
pronounced. Interestingly, the indie status itself shows no significant direct effect (coefficient = 0.009, p = 0.632), and release year variables remain non-significant.\
Model 8 introduces interaction terms between localisation and indie status, revealing a more nuanced relationship. When interactions are included, indie status becomes 
highly significant (coefficient = 0.261, p < 0.001), suggesting indie games with full localisation actually have higher Chinese review ratios than non-indie games. However, 
the significant negative interaction terms indicate this advantage diminishes or reverses for indie games with partial or no localisation.\
Model comparison metrics confirm the importance of these interactions: Model 8 shows improved fit with lower AIC (-33980.82 vs -33962.81), and the likelihood ratio 
test strongly supports the interaction model (χ² = 24.01, p < 0.001). The slightly higher BIC for Model 8 reflects the penalty for additional parameters but doesn't 
outweigh the explanatory benefits of including the interactions.\
Overall, these results suggest that localisation efforts have differential impacts on indie versus non-indie games, with indie developers potentially seeing stronger 
returns from comprehensive localisation investments.

# Models with Combined Chinese Localisation
```{r}
# Model with combined Chinese localisation (SC or TC)
model9 <- betareg(
  sc_ratio_adj ~ factor(full_localisation_combo) + release_year, 
  data = steam_data
)
summary(model9)

# Model with combined Chinese localisation + indie interaction
model10 <- betareg(
  sc_ratio_adj ~ factor(full_localisation_combo)*has_indie + release_year, 
  data = steam_data
)
summary(model10)

# Compare new models to previous ones
AIC(model4, model7, model8, model9, model10)
BIC(model4, model7, model8, model9, model10)

# LRT test for comparing nested models
lrt_result_910 <- lrtest(model9, model10)
print(lrt_result_910)

# Calculate odds ratios for model10
exp(coef(model10)[c(1:4, 20:21)])
```

The analysis examines how different levels of Chinese localisation (combining Simplified and Traditional Chinese) impact the ratio of Chinese reviews, 
with particular attention to interactions with indie game status.\
Model 9 demonstrates that localisation significantly affects Chinese review ratios. Compared to games with "Audio + Text" localisation, games with 
no Chinese localisation show dramatically lower Chinese review proportions (coefficient: -1.29, p<0.001), while "Text Only" games also demonstrate 
significantly lower proportions but to a lesser degree (coefficient: -0.19, p<0.001). Release year variables surprisingly show no significant impact 
across the entire period studied.\
Model 10 reveals interesting interactions between localisation and indie status. Indie games generally show higher Chinese review ratios (coefficient: 0.23, p<0.001), 
with the odds ratio indicating indie games have 1.26 times higher odds of attracting Chinese reviews than non-indie titles. However, significant negative interactions 
between indie status and localisation levels (both p<0.001) suggest the positive effect of being an indie game partially offsets the negative impact of having limited 
localisation.\
Model comparison metrics confirm the interaction model's superiority, with lower AIC (-34175.94 vs -34155.95) and a significant likelihood ratio test (p<0.001). The 
pseudo R-squared remains relatively consistent (0.290), suggesting localisation levels explain approximately 29% of the variance in Chinese review proportions when 
accounting for release year and indie status effects.

# Models with Genre Controls
```{r}
# Added genres dummy
model11 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year +
    has_action + has_adventure + has_rpg + has_story_rich + has_strategy + 
    has_casual + has_simulation + has_anime + has_puzzle,
  data = steam_data
)
summary(model11)

# Added log total review
model12 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year + log_total_reviews +
    has_action + has_adventure + has_rpg + has_story_rich + has_strategy + 
    has_casual + has_simulation + has_anime + has_puzzle,
  data = steam_data
)
summary(model12)

# Transfer coefficient to odds ratio
odds_model12 <- exp(coef(model12))
print(odds_model12)

# Compare new models to previous ones
AIC(model10, model11, model12)
BIC(model10, model11, model12)

# LRT test for comparing nested models
lrt_result_1112 <- lrtest(model11, model12)
print(lrt_result_1112)
```

The analysis incorporates genre-specific variables to examine how different game types influence Chinese review proportions.\
Model11 introduces nine game genre dummies alongside localisation variables and release year fixed effects. Localisation remains highly significant, 
with games having no Chinese localisation showing a substantial negative effect (-1.42) compared to games with both audio and text localisation. 
Several genres demonstrate significant influence on Chinese review ratios: RPG (+0.30), anime (+0.74), and strategy games (+0.17) show strong positive 
associations with higher Chinese review proportions, whilst action (-0.19) and simulation games (-0.16) show significant negative relationships. 
The model achieves a pseudo R-squared of 0.3316, explaining approximately one-third of the variance.\
Model12 extends this by incorporating the logarithm of total reviews, which proves highly significant (p < 2e-16) with a positive coefficient (0.038). 
This suggests that more popular games (those with more total reviews) tend to have higher proportions of Chinese reviews, after controlling for other factors. 
Including this variable marginally improves explanatory power (pseudo R-squared increases to 0.3365).\
Model comparison metrics (AIC, BIC) and a significant likelihood ratio test (p = 1.21e-10) confirm that Model12 represents a statistically significant 
improvement over previous models. The primary genre effects remain robust, indicating that Chinese players have distinct preferences for certain game 
types, particularly anime-themed and RPG titles.

# Factor Analysis for Genre Dimensionality Reduction
```{r}
# Create a binary tag matrix
tag_matrix <- steam_data %>%
  mutate(game_tags = as.character(game_tags)) %>%
  rowwise() %>%
  mutate(extracted_tags = list(extract_tags(game_tags))) %>%
  unnest(extracted_tags) %>%
  mutate(value = 1) %>%
  distinct(app_id, extracted_tags, .keep_all = TRUE) %>%
  pivot_wider(
    id_cols = app_id, 
    names_from = extracted_tags, 
    values_from = value,
    values_fill = 0
  )

# Count tag frequencies to identify prevalent tags (≥150 games)
tag_freq <- colSums(tag_matrix[, -1])
tags_to_keep <- names(tag_freq[tag_freq >= 150])
cat("Number of tags that appear in at least 150 games:", length(tags_to_keep), "\n")

# Filter the tag matrix to include only prevalent tags
tag_matrix_filtered <- tag_matrix[, c("app_id", tags_to_keep)]

# Check dimensions of filtered matrix
dim(tag_matrix_filtered)
```

```{r results='hide'}
set.seed(123)  # For reproducibility
tetra_cor <- tetrachoric(tag_matrix_filtered[, -1])$rho
```

```{r}
# Check for NA values in the correlation matrix (can happen with tetrachoric correlations)
sum(is.na(tetra_cor))
# If NAs exist, we might need to handle them
if(sum(is.na(tetra_cor)) > 0) {
  # Replace NAs with 0s for subsequent analyses
  tetra_cor[is.na(tetra_cor)] <- 0
}

# Kaiser-Meyer-Olkin (KMO) test for sampling adequacy
kmo_result <- KMO(tetra_cor)
print(kmo_result)

# Bartlett's test of sphericity
bartlett_result <- cortest.bartlett(tetra_cor, n = nrow(tag_matrix_filtered))
print(bartlett_result)

# Determine number of factors using parallel analysis
set.seed(123)  # For reproducibility
parallel_result <- fa.parallel(
  tetra_cor, 
  n.obs = nrow(tag_matrix_filtered),
  fa = "fa",
  cor = "cor",  # We're passing a correlation matrix
  n.iter = 20   # Reduce iterations for faster computation
)

# Extract 20 factors
set.seed(123)  # For reproducibility
n_factors <- 20

fa_result <- fa(
  tetra_cor,
  nfactors = n_factors,
  rotate = "varimax",  # Orthogonal rotation for better interpretability
  cor = "cor",  # We're using a correlation matrix
  n.obs = nrow(tag_matrix_filtered)
)

# Print factor loadings with a reasonable cutoff
print(fa_result$loadings, cutoff = 0.3)

# List of tags to exclude (platform features rather than genre characteristics)
platform_tags <- c(
  "Family Sharing", "Steam Achievements", "Steam Trading Cards", "Steam Cloud", 
  "Steam Workshop", "Full controller support", "Tracked Controller Support", 
  "Partial Controller Support", "Controller", "Steam Leaderboards", 
  "Remote Play Together", "Remote Play on TV", "Remote Play on Phone", 
  "Remote Play on Tablet", "Captions available"
)

# Filter out platform tags from tag matrix
platform_cols <- which(names(tag_matrix_filtered) %in% platform_tags)
tag_matrix_filtered_noplat <- tag_matrix_filtered[, -platform_cols]

# Check dimensions after removing platform tags
dim(tag_matrix_filtered_noplat)
```

```{r results='hide'}
# Compute tetrachoric correlation matrix for the refined set
set.seed(123)
tetra_cor_filtered <- tetrachoric(tag_matrix_filtered_noplat[, -1])$rho

# Replace any NAs with 0s
if(sum(is.na(tetra_cor_filtered)) > 0) {
  tetra_cor_filtered[is.na(tetra_cor_filtered)] <- 0
}

# Extract factors with a more reasonable number
n_factors <- 15  # Capturing around 50% of variance based on previous analysis
fa_result_refined <- fa(
  tetra_cor_filtered,
  nfactors = n_factors,
  rotate = "varimax",
  cor = "cor",
  n.obs = nrow(tag_matrix_filtered_noplat)
)
```

# Factor Interpretation and Naming
```{r}
# Function to extract top loading tags for each factor
get_top_loadings <- function(loadings_matrix, factor_num, n_tags = 20, cutoff = 0.3) {
  # Extract loadings for the specified factor
  factor_loadings <- loadings_matrix[, factor_num]
  
  # Find absolute loadings above cutoff
  significant_loadings <- abs(factor_loadings) >= cutoff
  
  # Get the tags with significant loadings
  significant_tags <- names(factor_loadings)[significant_loadings]
  significant_values <- factor_loadings[significant_loadings]
  
  # Create a data frame with tags and loadings
  result <- data.frame(
    Tag = significant_tags,
    Loading = round(significant_values, 3)
  )
  
  # Sort by absolute loading in descending order
  result <- result[order(-abs(result$Loading)), ]
  
  # Return top n tags
  return(head(result, n_tags))
}

# Create a consolidated view of the factors
factor_summary <- list()
for (i in 1:n_factors) {
  factor_summary[[i]] <- get_top_loadings(fa_result_refined$loadings, i)
}

# Print summaries for each factor
for (i in 1:n_factors) {
  cat(paste0("Factor ", i, " (", round(fa_result_refined$Vaccounted[2, i] * 100, 2), "% of variance)\n"))
  print(factor_summary[[i]])
  cat("\n")
}

# Assign factor names based on explicit matching to factor indices
factor_names <- rep(NA, n_factors)
factor_names[1] <- "City_Builders_Economic_Management_Sims"
factor_names[2] <- "Detective_Interactive_Narrative_Games"
factor_names[3] <- "Atmospheric_Retro_RPGs_Non_Mature"
factor_names[4] <- "Turn_Based_Tactical_Party_RPGs"
factor_names[5] <- "Couch_Co_Op_Local_Multiplayer_Games"
factor_names[6] <- "Free_to_Play_MMOs_Competitive_Online_Games"
factor_names[7] <- "Military_Strategy_War_Simulations"
factor_names[8] <- "Wholesome_Casual_Family_Friendly_Games"
factor_names[9] <- "Skill_Based_Action_RPGs_Souls_likes"
factor_names[10] <- "Immersive_3D_Simulations_Driving_Games"
factor_names[11] <- "Survival_Horror_Dark_Adventure"
factor_names[12] <- "Chaotic_Top_Down_Shooters_Roguelites"
factor_names[13] <- "Roguelike_Deckbuilders_Procedural_Indie_Games"
factor_names[14] <- "Sci_Fi_Space_Futuristic_Simulation"
factor_names[15] <- "Comedy_Dark_Humor"
```

# Creating Factor Scores
```{r}
# Get app_ids from the tag matrix
app_ids <- tag_matrix_filtered_noplat$app_id

# Calculate factor scores using Thurstone method as recommended
fa_scores <- factor.scores(
  tag_matrix_filtered_noplat[, -1],  # Exclude app_id column
  fa_result_refined,
  method = "Thurstone"
)

# Create a data frame with app_id and factor scores
fa_scores_df <- as.data.frame(fa_scores$scores)
colnames(fa_scores_df) <- factor_names  # Rename columns to factor names
fa_scores_df$app_id <- app_ids  # Add back the app_id column

# View the structure of the factor scores dataframe
str(fa_scores_df)

# Merge factor scores with original steam_data
steam_data_fa <- steam_data %>%
  left_join(fa_scores_df, by = "app_id")

# Check if key variables exist in the merged dataset
variables_check <- c("sc_localisation_combo", "full_localisation_combo", "release_year", "log_total_reviews") %in% 
  names(steam_data_fa)
print(paste("Variables present:", paste(c("sc_localisation_combo", "full_localisation_combo", 
                                          "release_year", "log_total_reviews"), 
                                        variables_check, sep = ": ", collapse = ", ")))

# Check for missing values in factor columns
factor_names <- colnames(fa_scores_df)[1:15]  # Get just the factor names
missing_values <- colSums(is.na(steam_data_fa[, factor_names]))
print(missing_values)
# No missing value
```

# Models with Factor Scores
```{r}
# MODEL13 with factor scores instead of genre dummies
model13 <- betareg(
  sc_ratio_adj ~ factor(full_localisation_combo) + release_year + log_total_reviews +
    City_Builders_Economic_Management_Sims +
    Detective_Interactive_Narrative_Games +
    Atmospheric_Retro_RPGs_Non_Mature +
    Turn_Based_Tactical_Party_RPGs +
    Couch_Co_Op_Local_Multiplayer_Games +
    Free_to_Play_MMOs_Competitive_Online_Games +
    Military_Strategy_War_Simulations +
    Wholesome_Casual_Family_Friendly_Games +
    Skill_Based_Action_RPGs_Souls_likes +
    Immersive_3D_Simulations_Driving_Games +
    Survival_Horror_Dark_Adventure +
    Chaotic_Top_Down_Shooters_Roguelites +
    Roguelike_Deckbuilders_Procedural_Indie_Games +
    Sci_Fi_Space_Futuristic_Simulation +
    Comedy_Dark_Humor,
  data = steam_data_fa
)

summary(model13)

# Transfer coefficient to odds ratio
odds_model13 <- exp(coef(model13))
print(odds_model13)

#Perform LR Test for model12 and model13
lrtest_1213 <- lrtest(model12, model13)
print(lrtest_1213)

# Compare models using AIC and BIC
AIC(model12, model13)
BIC(model12, model13)

# Compare pseudo R-squared
pseudo_r2_model12 <- summary(model12)$pseudo.r.squared
pseudo_r2_model13 <- summary(model13)$pseudo.r.squared

comparison <- data.frame(
  Model = c("Original (Model12)", "Factor Analysis (Model13)"),
  Pseudo_R_Squared = c(pseudo_r2_model12, pseudo_r2_model13),
  AIC = c(AIC(model12), AIC(model13)),
  BIC = c(BIC(model12), BIC(model13)),
  Parameters = c(length(coef(model12)), length(coef(model13)))
)
print(comparison)

# Check for multicollinearity among factors
if (requireNamespace("car", quietly = TRUE)) {
  vif_values <- car::vif(model13)
  print("Variance Inflation Factors (VIF):")
  print(vif_values)
}

# Test for significant factors
wald_test13 <- waldtest(model13)
print("Wald test for factor significance:")
print(wald_test13)
```

## Localization Effects

No localization significantly decreases the odds of Chinese reviews by 73% (OR = 0.27)、
Text-only localization decreases the odds by 18% (OR = 0.82)、
Having full localization (audio and text) serves as the reference category with the highest Chinese review proportion

## Positive Influences on Chinese Review Proportion

Roguelike Deckbuilders/Procedural Indie Games: Increases odds by 4.4% (OR = 1.045)\
Detective/Interactive Narrative Games: Increases odds by 4.0% (OR = 1.040)\
Turn-Based Tactical Party RPGs: Increases odds by 3.9% (OR = 1.039)\
Chaotic Top Down Shooters/Roguelites: Increases odds by 2.2% (OR = 1.022)\
Military Strategy/War Simulations: Increases odds by 2.1% (OR = 1.021)

## Negative Influences on Chinese Review Proportion

Atmospheric Retro RPGs: Strongest negative effect, decreasing odds by 15.5% (OR = 0.855)\
Immersive 3D Simulations/Driving Games: Decreases odds by 8.8% (OR = 0.912)\
Survival Horror/Dark Adventure: Decreases odds by 4.4% (OR = 0.956)\
Couch Co-Op/Local Multiplayer Games: Decreases odds by 4.2% (OR = 0.958)\
Comedy/Dark Humor: Decreases odds by 3.4% (OR = 0.966)\
Wholesome Casual Family Friendly Games: Decreases odds by 2.7% (OR = 0.973)

## Other Significant Factors

Total reviews (log): For every 10% increase in the total number of reviews, the odds of Chinese reviews increase by approximately 0.41% 
(log(1.1) ≈ 0.095, OR = 1.043^0.095 ≈ 1.0041)\
Release year: More recent releases generally show higher proportions of Chinese reviews, with years after 2016 showing positive effects

## Model Performance

Pseudo R-squared of 0.3405 (slightly higher than previous models)\
Strong statistical significance for most genre and localization factors\
Low multicollinearity among factors (VIF values generally below 1.1)

These findings reveal nuanced genre preferences among Chinese players that were not fully captured by the broader genre 
categorisations in previous models. The significant negative coefficient for Atmospheric Retro RPGs is particularly noteworthy, 
suggesting this genre category appeals less to Chinese players despite the broader RPG category showing positive effects in earlier models.\
The continued significance of log_total_reviews (0.042, p<0.001) confirms that game popularity remains positively associated with 
Chinese review proportion, independent of genre and localisation factors.

# Final Model with Significant Factors
```{r}
# MODEL14 with only significant factors from MODEL13
model14 <- betareg(
  sc_ratio_adj ~ factor(sc_localisation_combo) + release_year + log_total_reviews +
    Atmospheric_Retro_RPGs_Non_Mature +
    Immersive_3D_Simulations_Driving_Games +
    Roguelike_Deckbuilders_Procedural_Indie_Games +
    Survival_Horror_Dark_Adventure +
    Couch_Co_Op_Local_Multiplayer_Games +
    Detective_Interactive_Narrative_Games +
    Turn_Based_Tactical_Party_RPGs +
    Comedy_Dark_Humor +
    Wholesome_Casual_Family_Friendly_Games +
    Free_to_Play_MMOs_Competitive_Online_Games +
    Chaotic_Top_Down_Shooters_Roguelites +
    Military_Strategy_War_Simulations +
    City_Builders_Economic_Management_Sims,
  data = steam_data_fa
)
summary(model14)

# Compare all three models
AIC(model12, model13, model14)
BIC(model12, model13, model14)
```